Mitigating Low Audio Quality by Domain Transfer for Better ASR

### 2020-04-12 2020-tsd-brno-denoise/denoise.tex
tsd 2020 denoise: typos

Automatic speech recognition is generally approached by means of machine
learning: a statistical model is inferred based on some training data. Its
application bases on the assumption that whatever was learned about the training
data will also apply for the input data. It is clear then, that if the input
data have different properties than the training data, the basic assumption is
violated and the performance will suffer.
Also if the training data themselves are damaged in a way that makes the desired
information harder to extract, the learning is going to be less successful.

@@

What acoustic defects are actually present? Since the corpus was digitized from
magnetophone tapes of spontaneous talks by a single speaker recorded in various
amateur conditions and with consumer devices, we can broadly distinguist these
types of interefering signal:
\begin{enumerate}
\item{additive noise -- hum or hiss,}
\item{
    stationary interference like screeching added by low-quality magnetophone
    parts or the erasing head signal,
}
\item{non-stationary interference like like background speech or door slams,}
\item{
    room echo or ill-equalized microphone boosting or cutting certain
    frequencies,
}
\item{non-linear distortion of the magnetophone}
\item{speed fluctuations.}
\end{enumerate}

@@

The revolutionary article of Zhu et al. (2017)\cite{cyclegan} presenting
cycle-consistent generative adversarial networks gave mankind a mighty tool and
a hilarious tool that was used for de-hazing
photographs\cite{Engin_2018_CVPR_Workshops}, giving people other's facial
expressions\cite{jin2017faceoff}, in biomedicine\cite{yang2018biogan} and also
in speech processing: Kaneko and Tameoka (2017)\cite{kaneko2017parallel} present
speech domain transfer and Hosseini-Asl et al.
(2018)\cite{hosseini2018malevoicegan} do the same for the purpose of speech
recognition.

>>>>

Automatic speech recognition is generally approached by means of machine
learning: a statistical model is inferred based on some training data. Its
application bases on the assumption that whatever was learned about the training
data will also apply for the input data. It is clear then, that if the input
data have different properties than the training data, the basic assumption is
violated and the inference performance will suffer.
Also if the training data themselves are damaged in a way that makes the desired
information harder to extract, the learning is going to be less successful.

@@

What acoustic defects are actually present? Since the corpus was digitized from
magnetophone tapes of spontaneous talks by a single speaker recorded in various
amateur conditions and with consumer devices, we can broadly distinguist these
types of interefering signal:
\begin{enumerate}
\item{additive noise -- hum or hiss,}
\item{
    stationary interference like screeching added by low-quality magnetophone
    parts or the erasing head signal,
}
\item{non-stationary interference like background speech or door slams,}
\item{
    room echo or ill-equalized microphone boosting or cutting certain
    frequencies,
}
\item{non-linear distortion of the magnetophone}
\item{speed fluctuations.}
\end{enumerate}

@@

The revolutionary article of Zhu et al. (2017)\cite{cyclegan} presenting
cycle-consistent generative adversarial networks gave mankind a mighty tool and
a hilarious toy that was used for de-hazing
photographs\cite{Engin_2018_CVPR_Workshops}, giving people other's facial
expressions\cite{jin2017faceoff}, in biomedicine\cite{yang2018biogan} and also
in speech processing: Kaneko and Tameoka (2017)\cite{kaneko2017parallel} present
speech domain transfer and Hosseini-Asl et al.
(2018)\cite{hosseini2018malevoicegan} do the same for the purpose of speech
recognition.
